---
title: "match"
author: "Maita Schade"
date: "Aug 26, 2019"
output: html_notebook
---


Given a target sample, recoded panel, and possibly previous invites and completes, this notebook produces a new set of panelists to invite, with flexible number of columns (for larger batches).

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```

Set the space up. Country is the only thing you should need to set manually, if the files are all set up properly.
```{r}
country <- "AR"
```

Defining files--make sure the dirs are okay; other than that you shouldn't need to touch this if the file structure is set up properly.
```{r}
#strats = ("GEO1_AR2010")
#strat2 = "URBAN"
# wave = 17
# filedate = "190826"

datadir <- paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/Noam Argentina Panel/Matching process/Data/',country,'/')



panelfile <- paste0(datadir,'panel/', country, '_netquest_recoded.csv')

recodepath <- paste0("./recode_Netquest_IPUMS_",country, ".csv") #table specifying recodes
parampath <- "./country_parameters.csv" # set specefic parameters in this file

responsefile <- paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/Noam Argentina Panel/Data processing/Code/complete_ids.csv')
#file of not yet sent IDs
recyclefile <- paste0(datadir, "panel/AR_selected_wave1_QC.csv")
# completes
# previous selections
```


```{r}
library('MatchIt')
library('data.table')
library('openxlsx')
# library('labelled')
# 
# require(plyr)
# require(reshape2)
library(stringr)
```

Load country-specific parameters:
```{r}
params <- fread(parampath,key = "country")[country,]
target.date <- params[,target.date]
print(paste0("Target date is ", target.date))

NQ_id <- params[,NQ_id]


targetfile <- paste0(datadir, "sample/", country, "_target_", target.date, ".csv")
```




Load data
```{r}
target <- fread(targetfile, colClasses = c(sampleId="character"),drop = c("censusId"))
target[,sampleId:=str_pad(sampleId,width=13,pad="0")]
panel <- fread(panelfile)
if(exists("recyclefile")){
  recycle <- fread(recyclefile)
}
length(unique(panel$X))
length(unique(target$X))
```


Are there previous invites? If so, load them.
Also, prune the panel to just those not previously invited.
```{r}
if (length(list.files(path=paste0(datadir,"panel/"), pattern = "wave"))>0){
  print("previous invites found")
  # Printing what invites are considered
  cat(paste0("Included invite files: \n"))

  # Reading in invite files from all waves
  waves <- lapply(
    grep("QC",list.files(path=paste0(datadir,"panel/"), pattern = "wave"),
         invert = T, value = T), 
    function (x){
      cat(paste0("    ",x,"\n"))
    ## We make sure the individual waves have distinguishable names by attaching suffixes
  
      df<-fread(paste0(datadir, "panel/",x),colClasses = c(sampleId="character"))
      df[,sampleId := str_pad(string = sampleId, width = max(nchar(sampleId)), side = "left", pad = "0")]
      #df[,grep("panelId",names(df),value = T)]<-sapply(df[,grep("panelId",names(df),value = T)], tolower)
      nwave=as.numeric(str_match(x, "wave(\\d+)")[2])
      suffix=paste0(".",((nwave-1)*5)+1:(ncol(df)-1))
      print(suffix)
      names(df)[grep("panelId.?",names(df))] <- paste0("panelId",suffix)
      return(df)

   }
  )
  
  # The target is a table of target records, with selected panelist IDs for each wave
  target.select <- Reduce(function(dtf1, dtf2) {merge(dtf1, dtf2,
                                               by = c("sampleId"),
                                               all.x = TRUE)},
                   waves)
  
  # target <- target[names(target)[,-grep("targetId|X",names(target))]]
  
  # "selected" is a long list of all NQ panelists selected from our end
  selected.wide <- Reduce(function(dtf1, dtf2) {merge(dtf1, dtf2,
                                               by = c("sampleId"),
                                               all.x = TRUE, all.y = TRUE)},
                   waves)
  selected.wide
  # selected <- selected_wide[names(selected_wide)[-grep("targetId|X",names(selected_wide))]]
  selected <- melt(data = selected.wide,measure.vars = c(grep("panelId",names(selected.wide))))
  
  names(selected)<-c("sampleId",   "variable",   "panelId")
  selected[,batch:= as.integer(str_match(variable,"\\d\\d?"))]
  
  selected<-selected[selected[,!is.na(panelId)],]
  # selected$wave <- as.integer(regmatches(selected$variable, 
  #                                        regexpr("\\.\\K\\d+$",selected$variable,perl=TRUE)
  #                                        )
  #                             )

  # Remove who was _not_ invited
  names(recycle)[1] <- "panelId"

  # what is going on with more removals than recycled IDs?
  # I would expect that the number of recycles minus the number of duplicates equals the removals.
  if(exists("recycle")){
    # Remove who was _not_ invited
    names(recycle)[1] <- "panelId"
    actually.used <- (!(selected$panelId%in%recycle$panelId))|(selected$batch>5)
    nrow(selected)-sum(actually.used)
    
    
    invited <- selected[actually.used,]
    dim(invited)
  } else {
    invited <- selected
  }
  # Prune panel to exclude invited
  panel <- panel[!panelId %in% invited$panelId,]
  
  # set wave
  wave <- length(waves)+1
  

} else {wave <- 1}
```

Check that target.select and target are compatible (and nothing got somehow messed up when fixing to dept)
```{r}
#Are we okay--did we not mess up the sample when fixing depts?
sum(!target.select$sampleId%in%target$sampleId)==0
```


Are there previous completes? If so, load them.
```{r}
if (exists("responsefile")){
  print("completes found!")

  # # "responded" can be loaded straight from Qualtrics 
  responded <- fread(responsefile)
  # responded[,"panelId" := substr(ticket,1,16)]
  # responded <- responded[-(1:3),panelId]

  #... for identifying how many targets have been hit, attach to each respondent its unique SAMPID
  responded <- selected[panelId%in%responded$V2]
  responded <- responded[!duplicated(panelId,fromLast = TRUE),]
  

    
  # Counting duplicates by counting occurrence of sampleId in respondents:
  nsamp_resp <- table(responded$sampleId)
 
  dupes <- sum(nsamp_resp-1)  
  dupes
  
  legit <- nrow(responded)-dupes

  cat(paste0("\nDuplicates in ", country, ": ", dupes,"\n"))
  cat(paste0("\nLegit responses: ", legit))

  # # Respondents that were not invited?
  # cat(responded[is.na(responded$SAMPID),][[NQ_id]])
  
  ## Prune target to exclude filled slots
  # create list of respondents in wide sample id format--actually this shouldn't be necessary here, but let's not futz with it for now
  invited.resp <- invited[(panelId %in% responded$panelId),] #those that were invited and actually responded
  responded.wide <- dcast(invited.resp, ... ~ variable)
  # responded.wide[sampleId%in%sampleId[duplicated(sampleId)]]
  
  
  # Check that no sampleId's are duplicated:
  if (sum(duplicated(responded.wide$sampleId))!= 0){
    print("Alert! Somehow you have duplicated sampleIds!")
    }
  
  # keep only targets that are not included in response set
  target.pruned <- target[!sampleId%in%responded.wide$sampleId,]
  dim(invited.resp)
  dim(responded)
  dim(responded.wide)
  print("Dimensions of pruned target:")
  dim(target.pruned)
} else {
  target.pruned <- target
  }

```



Add a treatment into it:
```{r}
panel[,'treat':= rep(0,nrow(panel))]
target.pruned[,'treat':=rep(1,nrow(target.pruned))]
```

Now join this data together:
```{r}
alldata <- rbind(panel, target.pruned, fill=T)
#fill NA
alldata[is.na(panelId),panelId:="9999999999"]
alldata[is.na(sampleId),sampleId:="9999999999"]

head(alldata)
```

Divide target sample into age quantiles (in this case, deciles) and add that to the data:
```{r}
age_q <- quantile(target$age,prob = seq(0,1,0.1)) #this is the full target
alldata[,'age_group' :=  as.integer(cut(alldata$age,breaks = age_q, include.lowest = TRUE))]
alldata[is.na(age_group),age]
alldata$age_group[is.na(alldata$age_group)] <- 10 #highest age-group can get lost; fill it in
```


Load in matching.vars from recodefile
```{r}
recode_map <- fread(recodepath)
matching.vars <- unique(recode_map$common_var)
```

Now carry out the matching. 
```{r}
matching.form <- as.formula(paste0("treat ~ ", paste(matching.vars, collapse=' + ')))
```


We'll have to repeat this process (at least for everything except PS). 
* start empty dataframe initialized with target IDs
* make a copy of the data to alter
* for each i in range:
  + run the matching
  + store the matched IDs
  + store some overall metrics about the match
  + reduce the panel data
* return the match objects

```{r}
matchRatio <- function(data, metric, n, exact = c()){
  # A wrapper for the MatchIt framework to carry out arbitrary numbers of successive matches
  # data must have:
  #   * sampleId
  #   * panelId
  #   * treat
  require(MatchIt)
    
  # assign the dataframe to hold the matching results
  df <- data.frame(matrix(ncol=1, nrow=sum(data$treat==1)))
  names(df) <- c("sampleId")
  df$sampleId <- data$sampleId[data$treat==1]
  
  # assign the object to hold all the matching information
  matches <- vector("list",n)
  
  # make a copy of the passed-in data
  data.copy <- data.frame(data)
  
  # loop over the number of respondents per target
  # if there are issues, can I relax the age groups?
  for(i in 1:n){
    print(paste('i = ',as.character(i)))
    m <- matchit(matching.form, 
                 data = data.copy, exact=exact, method = "nearest", distance = metric)
    controls <- match.data(m, group='control')
    
    try({matches[[i]] <- m
        sampleids <- data.copy[row.names(m$match.matrix), "sampleId"]
        panelids <- data.copy[m$match.matrix,"panelId"]
        ids <- data.frame(sampleId=sampleids, panelId=panelids, stringsAsFactors = F)
        df <- merge(x=df, y=ids, by="sampleId", all.x = TRUE, suffixes=c("",as.character(i)))
        } 
    )
    data.copy <- data.copy[!data.copy$panelId %in% controls$panelId,] # not relying on rownames
    
  }
  return(list("ids"=df, "matches"=matches))
}

```



```{r}
n <- 5
matches = matchRatio(alldata, "mahalanobis", n, exact = c("age_group","gend"))
```

Save the id's of the matches to a file
```{r}
write.csv(
  matches$ids, 
  file=paste0(datadir,"panel/",country,"_selected_wave",wave,"_",format(Sys.time(),"%y%m%d"),".csv"),
  row.names = F)
wave
```

Do I have a good number of discrete location codes?
```{r}
length(unique(panel$X))
length(unique(target$X))
```

What are these NAs? --oh, it was the censusId! fixed now.
```{r}
lapply(names(alldata), function(x){
  print(x)
  alldata[is.na(alldata[[x]]),]
  })
```
What does the sample look like?
```{r}
set <- matches$ids
set <- Reduce(x = set[,grep("panelId",names(set),value = T)],f = append)
set <- panel[panelId%in%set,]

hist(target.pruned$gend)
hist(set$gend)
```
```{r}
target.pruned[,censusId:=substr(sampleId,1,12)]
target.pruned[,PERNUM:=substr(censusId,11,12)]
target.pruned[,SERIAL:=substr(censusId,1,10)]
write.csv(target.pruned,paste0("pruned_target_",format(Sys.time(),"%y%m%d"),".csv"))
write.csv(set,paste0("selected_IDs_",format(Sys.time(),"%y%m%d"),".csv"))
```

What does it look like, compared to the old sample?
```{r}
sample.old <- fread("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/Noam Argentina Panel/Matching process/Data/AR/sample/AR_target_20190909.csv")
hist(sample.old$age)
hist(target$age)
```




