---
title: "sample-matching_IPUMS-NQ_AR"
author: "Maita Schade"
date: "May 16, 2019"
output: html_notebook
---


run: *Ctrl+Shift+Enter*. 
New chunk: *Ctrl+Alt+I*.
*Ctrl+Shift+K* to preview the HTML file.

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```

```{r}
country = "BR"
strat1 = "GEO1_BR2010"
strat2 = "URBAN"
NQ_id  = "gp_codigo"

setwd(
  paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country)
)
```


A word or two about feasibility. The only census information we can get is from IPUMS (it seems), and for the countries we are considering, these are the most recent:

country   IPUMS   census    weighted
Peru      2007    2017      No
Brazil    2010    2010      Yes
Chile     2002    2017      No
Mexico    2015    2010      Yes
          (IPUMS intercensal survey)
Argentina 2010    2010      No
Colombia  2005    2018      Yes

Reading in the sampling data and making necessary updates.

Here, we are using the IPUMS data.

```{r}
load(paste0(country,"_data_loaded.RData"))
```

```{r}
select = read.csv(file=paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country,"/panel/matches_cem-mah.csv"))
```

```{r}
library('plyr')

census$ed <- rep(NA, length=length(census$EDUCBR))
census$ed[census$EDUCBR==0] <- 1
census$ed[census$EDUCBR>=1000 & census$EDUCBR<=2140] <- 2
census$ed[(census$EDUCBR==2141)|(census$EDUCBR==2190)] <- 3
census$ed[(census$EDUCBR>=2210 & census$EDUCBR<=2230)|census$EDUCBR==2900] <- 4
census$ed[(census$EDUCBR==2241)|(census$EDUCBR==2290)] <- 5
census$ed[census$EDUCBR>=3100 & census$EDUCBR<=3200] <- 6
census$ed[census$EDUCBR %in% c(3300, 3900)] <- 7
census$ed[census$EDUCBR %in% c(4170, 4180)] <- 8
census$ed[census$EDUCBR==4190] <- 9
census$ed[census$EDUCBR %in% c(4270, 4280)] <- 10
census$ed[census$EDUCBR %in% c(4230, 4240)] <- 11
census$ed[census$EDUCBR %in% c(4250, 4260)] <- 12

netquest$ed <- as.integer(netquest$BR_education_level_full)
```


```{r}
target <- join(select, census, by=c('SERIAL','PERNUM'))
sample <- join(select, netquest, by=NQ_id)
```

```{r}
age_q <- quantile(target$AGE,prob = seq(0,1,0.1))
sample['age_group'] <- as.integer(cut(sample$panelistAge,breaks = age_q, include.lowest = TRUE))
target['age_group'] <- as.integer(cut(target$AGE,breaks = age_q, include.lowest = TRUE))
#alldata$age_group[is.na(alldata$age_group)] <- 10
age_q
```

Age
```{r}
hist(census$AGE, breaks=9)
hist(sample$panelistAge)
hist(target$AGE)
```

education
```{r}
hist(census$ed)
hist(target$ed, breaks=7)
hist(sample$ed, breaks=7)
```
```{r}
table(sample$ed)
```

```{r}
table(target$ed)
```


