---
title: "sample-matching_IPUMS-NQ_MX, wave 16 'Blitz'"
author: "Maita Schade"
date: "Aug 15, 2019"
output: html_notebook
---


run: *Ctrl+Shift+Enter*. 
New chunk: *Ctrl+Alt+I*.
*Ctrl+Shift+K* to preview the HTML file.

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```

```{r}
country = "MX"
```
  

If using previously loaded census data, load here:
```{r}
load(paste0(country,"_data_loaded.RData"))
```

```{r}
strat1 = "GEO1_MX2015"
strat2 = "URBAN"
NQ_id  = "gp_codigo"
wave = 16
filedate = "190814"

wd<-paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country)
```


```{r}
library('MatchIt')
library('openxlsx')
library('labelled')

require(plyr)
require(reshape2)
require(stringr)
```

Load required data
```{r}
# census<- read.csv(
#   paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/',country,'/sample/',country,'_ipums-census_geo.csv')
#  )
# 
# netquest <- read.csv(
#   paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",
#   country,
#   "/panel/", country, "_netquest-panel_geo.csv")
# )
# save.image(paste0(country,"_data_loaded.RData"))
```

The selected target, and the recorded responses:
```{r}
# Printing what invites are considered
cat(paste0("Included invite files: \n"))

# Reading in invite files from all waves
waves <- lapply(list.files(path=paste0(wd,"/panel/"), pattern = "wave"), function (x){
  cat(paste0("    ",x,"\n"))
## We make sure the individual waves have distinguishable names by attaching suffixes
  
  df<-read.csv(paste0(wd, "/panel/",x),as.is = T) #c(NQ_id,"SERIAL","PERNUM"))
  df[names(df)[grep(NQ_id,names(df))]]<-sapply(df[names(df)[grep(NQ_id,names(df))]], tolower)
  nwave=as.numeric(str_match(x, "wave(\\d+)")[2])
  suffix=paste0(".",nwave+0:(ncol(df)-5))
  names(df)[grep(NQ_id,names(df))] <- paste0(NQ_id,suffix)
  return(df)
 }
)
```

```{r}
# Creating a single distinguishable sample ID for each individual target record
# make sure, if ever reusing this code, that SERIAL and PERNUM are not longer than anticipated
waves <- lapply(waves,function(x){
  x$SAMPCT <- rep(1, nrow(x))
  x$SAMPID <- paste0(
    sprintf('%010.0f',x$SERIAL),
    sprintf('%03.0f',x$PERNUM)
  )
## Individual person records that were drawn multiple times due to weighting will have a higher sample count
  for (i in unique(x[duplicated(x$SAMPID),'SAMPID'])){
    x[x$SAMPID==i,'SAMPCT']<- 1:length(x[x$SAMPID==i,'SAMPCT'])
  }
  return(x)
  }
  #x[NQ_id] <- sapply(x[NQ_id], tolower)
)

# The target is a table of target records, with selected panelist IDs for each wave
target <- Reduce(function(dtf1, dtf2) {merge(dtf1, dtf2, 
                                             by = c("SAMPID","SAMPCT","SERIAL","PERNUM"), 
                                             all.x = TRUE)},
                 waves)
target <- target[names(target)[-grep("targetId|X",names(target))]]

# "selected" is a long list of all NQ panelists selected from our end
selected_wide <- Reduce(function(dtf1, dtf2) {merge(dtf1, dtf2, 
                                             by = c("SAMPID","SAMPCT","SERIAL","PERNUM"), 
                                             all.x = TRUE, all.y = TRUE)},
                 waves)
selected <- selected_wide[names(selected_wide)[-grep("targetId|X",names(selected_wide))]]
selected <- melt(data = selected,measure.vars = c(grep(NQ_id,names(selected))))
names(selected)<-c("SAMPID",   "SAMPCT",   "SERIAL",   "PERNUM",   "variable", NQ_id)
selected<-selected[!is.na(selected[[NQ_id]]),]
selected$wave <- as.integer(regmatches(selected$variable, 
                                       regexpr("\\.\\K\\d+$",selected$variable,perl=TRUE)
                                       )
                            )
```

```{r}
table(target$SAMPID)[table(target$SAMPID)>1] #check this! if there are duplicates I need to get clever
```

```{r}

# "responded" are just all the IDs NQ has recorded responding to our survey
responded <- read.xlsx(
paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",
country,
"/panel/", country,"_complete_",filedate,".xlsx")
)
names(responded) <- c(NQ_id)
responded[[NQ_id]]<-sapply(responded[[NQ_id]], tolower)

#... for identifying how many targets have been hit, attach to each respondent its unique SAMPID
responded <- join(x=responded,y=selected, by=NQ_id)
responded$ID <- paste0(responded$SAMPID,responded$SAMPCT)

table(target$SAMPID)[table(target$SAMPID)>1] #check this! if there are duplicates I need to get clever
responded[responded$SAMPID=="0322156000002"&responded$wave>9,]
# thankfully the duplicates were knocked out earaly so we can proceed.

# Updating selected by wiping out the unused gp_codigos here--
# --if someone responded, we don't invite for that SAMPID for the following waves
apply(responded[responded$wave>=9,c(NQ_id,"SAMPID","wave")],1,
      function(r){
        selected[selected$wave>as.integer(r[["wave"]]) & selected$SAMPID==r[["SAMPID"]],NQ_id] <- NA
        assign('selected',selected,pos=.GlobalEnv)
        return(invisible())
      }
      )
```

```{r}
# Accounting for intentional "duplicates" due to weights by counting each ID in target and responses:
nsamp_resp <- table(responded$SAMPID) 
nsamp_targ <- table(target$SAMPID)

dupes <- sum(sapply(names(nsamp_resp), function(x){
  if (nsamp_resp[x]>nsamp_targ[x]){
    #cat(x, "\n")
    nsamp_resp[x]-nsamp_targ[x]
    } 
  else {0}
  }))

legit <- nrow(responded)-dupes

cat(paste0("\nDuplicates in ", country, ": ", dupes,"\n"))
cat(paste0("\nLegit responses: ", legit))
```


Respondents that were not invited:
```{r}
cat(responded[is.na(responded$SAMPID),][[NQ_id]])
```


Prune panel to exclude invited
```{r}
netquest <- netquest[! (netquest[[NQ_id]] %in% selected[[NQ_id]]),]
```

Prune target to exclude filled slots
```{r}
# create list of respondents in wide sample id format
selected_resp <- selected[(selected[[NQ_id]] %in% responded[[NQ_id]]),] #those that were invited and actually responded
resp_wide <- reshape(selected_resp[-grep("wave",names(selected_resp))], idvar = c("SAMPID","SAMPCT","SERIAL","PERNUM"), timevar = "variable", direction = "wide")
names(resp_wide)<-names(target[1:length(names(resp_wide))])
# count desired and achieved occurrence of each sample ID (filling in zeros) 
nsamp_targ <- table(target$SAMPID)      #counts for each SAMPID in target
nsamp_resp <- table(resp_wide$SAMPID)   #counts for each SAMPID in actual responses
nsamp_resp[target$SAMPID[!target$SAMPID%in%resp_wide$SAMPID]]<-0  #if SAMPID wasn't collected at all yet, resp. = 0

# I want the SAMPIDs that have fewer occurrences in the response set than in the target.
target_pruned <- target[nsamp_resp[target$SAMPID]<nsamp_targ[target$SAMPID],]
```



Double-check any sample IDs that have a response already but are being re-invited--make sure they are desired more than once.
```{r}
print(sum(target_pruned$SAMPID%in%resp_wide$SAMPID))
target_pruned[target_pruned$SAMPID%in%resp_wide$SAMPID,]
cat(nsamp_resp[unique(target_pruned[target_pruned$SAMPID%in%resp_wide$SAMPID,]$SAMPID)])
```
Cutting just the bits of the census we need going forward:
```{r}
print(dim(target_pruned))
tmp <- join(target_pruned[c('SERIAL','PERNUM')], census, by=c('SERIAL','PERNUM'))
print(dim(tmp))
census <- tmp
```



We have to recode the various characteristics we have at our disposal.
```{r}
matching.vars <- c('gend', 
                   'age', 
                   'ed', 
                   'ed_hhh', 
                   'emp', 
                   'emp_hhh', 
                   'auto',
                   'pc',
                   'web',
                   'lightbulb',
                   'floors', 
                   'nrooms',
                   'shower',
                   'tv',
                   'child',
                   'marst',
                   'pern',
                   'hhtype',
                   'hhh',
                   'X',
                   'Y'
                   )
                   
#Gender:          is fine.
census$gend <- census$SEX
netquest$gend <- netquest$p_sexo

#Age:          is fine, need to filter these to make sure we exclude too young respondents.
census$age <- mapvalues(census$AGE, from=c(999), to=c(NA))
netquest$age <- netquest$panelistAge
netquest$age[netquest$panelistAge>100] <- 100


#Education:    
census$ed <- rep(NA,length=length(census$EDUCMX))
census$ed[census$EDUCMX== 10] <- 1
census$ed[census$EDUCMX>= 20 & census$EDUCMX<= 29] <- 2
census$ed[census$EDUCMX>=100 & census$EDUCMX<=109] <- 3
census$ed[census$MX2015A_EDLEVEL==2] <- 4
census$ed[census$EDUCMX>=200 & census$EDUCMX<=229] <- 5
census$ed[census$MX2015A_EDLEVEL==3] <- 6
census$ed[census$MX2015A_EDLEVEL%in%c(6,7,8,9)] <- 7
census$ed[census$EDUCMX>=300 & census$EDUCMX<=339] <- 8
census$ed[census$MX2015A_EDLEVEL%in%c(4,5)] <- 9
census$ed[census$EDUCMX>=610 & census$EDUCMX<=619] <- 10
census$ed[census$MX2015A_EDLEVEL%in%c(10,11)] <- 11
census$ed[census$MX2015A_EDLEVEL%in%c(12,13)] <- 12
census$ed[census$MX2015A_EDLEVEL==14] <- 13

netquest$ed <- mapvalues(netquest$MX_education_level_merge,
                         from=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14),
                         to  =c(1,2,3,4,5,6,7,7,8, 9,10,11,12,13)
                         )

#Need head of household, as well
census$ed_hhh <- rep(NA,length=length(census$EDUCMX_HEAD))
census$ed_hhh[census$EDUCMX_HEAD== 10] <- 1
census$ed_hhh[census$EDUCMX_HEAD>= 20 & census$EDUCMX_HEAD<= 29] <- 2
census$ed_hhh[census$EDUCMX_HEAD>=100 & census$EDUCMX_HEAD<=109 & census$MX2015A_EDLEVEL_HEAD<2] <- 3
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD==2] <- 4
census$ed_hhh[census$EDUCMX_HEAD>=200 & census$EDUCMX_HEAD<=229 & census$MX2015A_EDLEVEL_HEAD< 3] <- 5
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD==3] <- 6
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(6,7,8,9)] <- 7
census$ed_hhh[census$EDUCMX_HEAD>=300 & census$EDUCMX_HEAD<=339 & census$MX2015A_EDLEVEL_HEAD< 4] <- 8
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(4,5)] <- 9
census$ed_hhh[census$EDUCMX_HEAD>=610 & census$EDUCMX_HEAD<=619 & census$MX2015A_EDLEVEL_HEAD<10] <- 10
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(10,11)] <- 11
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(12,13)] <- 12
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD==14] <- 13

netquest$ed_hhh <- mapvalues(netquest$MX_education_level_hhousehold_merge,
                         from=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14),
                         to  =c(1,2,3,4,5,6,7,7,8, 9,10,11,12,13)
                         )

    

#Employment. RECONSIDER ORDERING.
census$emp <- rep(NA,length=length(census$EDUCMX_HEAD))
census$emp[census$MX2015A_EMPSTAT%in%c(10,12,16)] <- 1 
census$emp[census$MX2015A_CLASSWK%in%c(4,5)] <- 1     # Trabajo actualmente por cuenta propia
census$emp[census$MX2015A_EMPSTAT%in%c(11,13,14,15)] <- 3 
census$emp[census$MX2015A_CLASSWK%in%c(1,2,3)] <- 2   # Trabajo actualmente como empleado
census$emp[census$MX2015A_EMPSTAT== 31] <- 3          # Estudiante (sin trabajar)
census$emp[census$MX2015A_EMPSTAT== 20] <- 4          # Desempleado
census$emp[census$MX2015A_EMPSTAT== 32] <- 5          # Retirado/Pensionista
census$emp[census$MX2015A_EMPSTAT== 34] <- 6          # Incapacitado
census$emp[census$MX2015A_EMPSTAT== 33] <- 7          # Labores del hogar
census$emp[census$MX2015A_EMPSTAT== 35] <- 7          # Did not work--assume that means they did housework

netquest$emp <- mapvalues(netquest$MX_laboral_situation,
       from=c(1,2,3,4,5,6,7,8,9),
       to=  c(1,2,3,4,4,5,5,6,7))

#  Employment of head of household: see above
census$emp_hhh <- rep(NA,length=length(census$EDUCMX_HEAD))
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD%in%c(10,12,16)] <- 1 
census$emp_hhh[census$MX2015A_CLASSWK_HEAD%in%c(4,5)] <- 1     # Trabajo actualmente por cuenta propia
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD%in%c(11,13,14,15)] <- 3 
census$emp_hhh[census$MX2015A_CLASSWK_HEAD%in%c(1,2,3)] <- 2   # Trabajo actualmente como empleado
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 31] <- 3          # Estudiante (sin trabajar)
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 20] <- 4          # Desempleado
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 32] <- 5          # Retirado/Pensionista
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 34] <- 6          # Incapacitado
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 33] <- 7          # Labores del hogar
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 35] <- 7          # Did not work--assume that means they did housework

netquest$emp_hhh <- mapvalues(netquest$MX_laboral_situation_hhousehold,
       from=c(1,2,3,4,5,6,7,8,9),
       to=  c(1,2,3,4,4,5,5,6,7))

#Auto
census$auto <- mapvalues(census$AUTOS,
        from=c(0,7,8,9),
        to=  c(2,1,NA,NA))
netquest$auto <- mapvalues(netquest$MX_NSE_cars,
       from=c(1,2,3,4),
       to=  c(2,1,1,1))

#Computer?
census$pc <- mapvalues(census$COMPUTER, 
                       from=c(0,1,2,9), 
                       to=c(NA,2,1,NA))
netquest$pc <- mapvalues(netquest$MX_NSE_computer,
                         from=c(1,2,3),
                         to  =c(2,1,1)
                         )

#Internet?
census$web <- mapvalues(census$INTERNET, from=c(0,1,2,9), to=c(NA,2,1,NA))
netquest$web <- mapvalues(netquest$MX_NSE_internet_at_home, from = c(1,2), to=c(1,2))

#Lightbulbs?
census$lightbulb <- rep(NA,length=length(census$MX2015A_LIGHTBULB))
census$lightbulb[census$MX2015A_LIGHTBULB>= 0 & census$MX2015A_LIGHTBULB<= 5] <- 1
census$lightbulb[census$MX2015A_LIGHTBULB>= 6 & census$MX2015A_LIGHTBULB<=10] <- 2
census$lightbulb[census$MX2015A_LIGHTBULB>=11 & census$MX2015A_LIGHTBULB<=15] <- 3
census$lightbulb[census$MX2015A_LIGHTBULB>=16 & census$MX2015A_LIGHTBULB<=20] <- 4
census$lightbulb[census$MX2015A_LIGHTBULB>=21 & census$MX2015A_LIGHTBULB<=90] <- 5

netquest$lightbulb <- netquest$MX_NSE_lights


#When going numeric, must replace NA with the average
census$floors <- mapvalues(census$MX2015A_FLOOR,
        from=c(1, 2, 3, 8, 9),
        to=  c(1, 1, 2,NA,NA))
netquest$floors <- mapvalues(netquest$MX_NSE_pavement,
        from=c(1, 2),
        to=  c(1, 2))

#Number of rooms
census$nrooms <- rep(NA,length=length(census$MX2015A_ROOMS))
census$nrooms[census$MX2015A_ROOMS<7] <- census$MX2015A_ROOMS[census$MX2015A_ROOMS<7]
census$nrooms[census$MX2015A_ROOMS>=7 & census$MX2015A_ROOMS<=20] <- 7 

netquest$nrooms <- netquest$MX_NSE_rooms

#Shower?
census$shower <- rep(NA,length=length(census$MX2015A_SHOWER))
census$shower[census$MX2015A_SHOWER<3] <-  census$MX2015A_SHOWER[census$MX2015A_SHOWER<3]

netquest$shower <- netquest$MX_NSE_shower

#Number of TVs
census$tv[census$MX2015A_TV%in%c(1,2)] <- census$MX2015A_TV[census$MX2015A_TV%in%c(1,2)]
netquest$tv <- mapvalues(netquest$MX_NSE_tv,
                         from=c(1,2,3,4),
                         to  =c(2,1,1,1)
                         )

#Children
census$child<-rep(NA, length=length(census$NCHILD))
census$child[census$NCHILD<=7] <- census$NCHILD[census$NCHILD<=7]
census$child[census$NCHILD>7] <- 7

netquest$child <- netquest$number_P3
netquest$child[netquest$P3==2] <- 0


#Marital status: need P1 from Netquest!
census$marst <- mapvalues(census$MARST,
                          from=c(1,2,3,4,9),
                          to  =c(1,4,2,3,NA)
                          )

netquest$marst <- mapvalues(netquest$P1,
                          from=c(1,2,3,4),
                          to  =c(1,4,2,3)
                          )

#number of persons in household
census$pern <- census$PERSONS
netquest$pern <- netquest$P2

#type of household
census$hhtype <- mapvalues(census$HHTYPE,
                          from=c(1,5,6,7,8,2,3,4,11,99, 0),
                          to  =c(1,5,5,6,6,2,4,3, 0, 0,NA)
                          )

netquest$hhtype <- mapvalues(netquest$P8,
                          from=c(1,2,3,4,5,6,7,99),
                          to  =c(1,5,6,2,4,3,5, 0)
                          )

#head of household?
census$hhh <- rep(NA,length=length(census$RELATE))
census$hhh[census$RELATE>1] <- 2
census$hhh[census$RELATE==1] <- 1

netquest$hhh <- mapvalues(netquest$P12,
                          from=c(1,2,3),
                          to  =c(1,2,1)
                          )
```

Give ID to both datasets, so we can go back to IDs when necessary
```{r}
census$id <- seq(dim(census)[1])
netquest$id <- seq(dim(netquest)[1])
```


If we do some non-numeric matching, we'd want to adjust the labels/levels.
```{r}
panel <- to_factor(netquest[append(matching.vars, c('id'))],
                   drop_unused_labels = TRUE)

panel['Fakeid'] <- netquest[[NQ_id]]
panel <- panel[panel$age>17,]

panel <- na.omit(panel)   
```

ADJUST FOR COUNTRY!
```{r}
census.proc <- to_factor(census[append(matching.vars,c(
                                          strat2,
                                          'PERWT',
                                          strat1,'id', 'SERIAL','PERNUM'))], drop_unused_labels = TRUE)
census.proc <- census.proc[census.proc$age>17,]

census.proc <- na.omit(census.proc)
census.proc <- census.proc[order(census.proc[strat1],census.proc[strat2]),]
```

Re-load the target with census info
```{r}
target_pruned <- census.proc
target_pruned <- target_pruned[!names(target_pruned) %in% c('SERIAL','PERNUM')]
target_pruned['Fakeid'] <- as.integer(rep(999999, length(target_pruned$age)))
```


Add a treatment into it:
```{r}
panel['treat'] <- rep(0,length(panel$age))
target_pruned['treat'] <- rep(1,length(target_pruned$age))
```


Now join this data together:
```{r}
# add a level to the alldata fakeid to accommodate the target
levels(panel$Fakeid) <- c(levels(panel$Fakeid),999999)
alldata<-rbind(panel,target_pruned[names(panel)])

#jointId will be the sequence number in the joint dataframe -- MAY NOT NEED THIS?
alldata$jointId <- seq(dim(alldata)[1])
rownames(alldata) <- alldata$jointId

```


Divide target sample into age quantiles (in this case, deciles) and add that to the data:
```{r}
age_q <- quantile(census.proc$age,prob = seq(0,1,0.1))
alldata['age_group'] <- as.integer(cut(alldata$age,breaks = age_q, include.lowest = TRUE))
alldata$age_group[is.na(alldata$age_group)] <- 10
```

#for the methods that require numeric approximation
```{r}
alldata_num<-data.frame(lapply(alldata, as.numeric))
```

Now the matching begins. This is using the MatchIt package as we are used to...
```{r}
matching.form <- as.formula(paste0("treat ~ ", paste(matching.vars, collapse=' + ')))
```

We'll have to repeat this process (at least for everything except PS), since the memory can't deal with all of this. 
* start empty dataframe initialized with target IDs
* make a copy of the data to alter
* for each i in range:
  + run the matching
  + store the matched IDs
  + store some overall metrics about the match
  + reduce the panel data
* return the match objects

```{r}
matchRatio <- function(data, metric, n, exact = c()){
  
  # assign the dataframe to hold the matching results
  df <- data.frame(matrix(ncol=1, nrow=sum(data$treat==1)))
  names(df) <- c("targetId")
  df$targetId <- data$id[data$treat==1]
  
  # assign the object to hold all the matching information
  matches <- vector("list",n)
  
  # make a copy of the passed-in data
  data.copy <- data.frame(data)
  
  
  # loop over the number of respondents per target
  # if there are issues, can I relax the age groups?
  for(i in 1:n){
    print(paste('i = ',to_character(i)))
    m <- matchit(matching.form, 
                 data = data.copy, exact=exact, method = "nearest", distance = metric)
    
    try({matches[[i]] <- m
        targetids <- data.copy[row.names(m$match.matrix), "id"]
        panelids <- as.data.frame(data.copy[m$match.matrix,"id"])
        names(panelids)<-c("panelId")
        panelids['targetId']<-targetids
        df <- merge(x=df, y=panelids, by="targetId", all.x = TRUE, suffixes=c("",to_character(i)))
        } #... maybe merge instead might be safer?
    )
    
    controls <- match.data(m, group='control')
    data.copy <- data.copy[!data.copy$jointId %in% controls$jointId,] # not relying on rownames
    
  }
  return(list("ids"=df, "matches"=matches))
}

```

```{r}
n <- 5
matches.cem_mah = matchRatio(alldata_num, "mahalanobis", n, exact = c("age_group","gend"))
```


Save the id's of the matches to a file, so I don't lose them--just in case
```{r}
tmp <- matches.cem_mah$ids

# attaching NQ panel code
for (i in c(1:n)){
  s <- ifelse(i>1, i,"")
  print(i)
  print(paste0("panelId",s))
  
  tmp[paste0(NQ_id,i)] <- merge(x = matches.cem_mah$ids, 
                    y = alldata[alldata$treat==0, c("Fakeid",'id')], 
                    by.x = paste0("panelId",s), 
                    by.y = "id")[["Fakeid"]]
  }


# attaching census identification, just in case!
tmp[c("SERIAL","PERNUM")] <- merge(x = matches.cem_mah$ids,
                                   y = census[c("SERIAL","PERNUM","id")],
                                   by.x = 'targetId',
                                   by.y = 'id')[c("SERIAL","PERNUM")]

write.csv(x=tmp[c(c("targetId"),paste0(NQ_id,c(1:n)), c("SERIAL","PERNUM"))], file=paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country,"/panel/",country,"_selected_wave",wave,"_",filedate,".csv"))
```

```{r}
sum(tmp$gp_codigo%in%selected$gp_codigo)
dim(target_pruned)
dim(tmp)
dim(responded)
```





