---
title: "sample-matching_IPUMS-NQ_BR"
author: "Maita Schade"
date: "May 13, 2019"
output: html_notebook
---


run: *Ctrl+Shift+Enter*. 
New chunk: *Ctrl+Alt+I*.
*Ctrl+Shift+K* to preview the HTML file.

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```

```{r}
country = "BR"
strat1 = "GEO1_BR2010"
strat2 = "URBAN"
NQ_id  = "gp_codigo"

setwd(
  paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country)
)
```


```{r}
library('MatchIt')
library('haven')
library('openxlsx')
library('labelled')
library(zoo)

require('cem')
require('plyr')
```

A word or two about feasibility. The only census information we can get is from IPUMS (it seems), and for the countries we are considering, these are the most recent:

country   IPUMS   census    weighted
Peru      2007    2017      No
Brazil    2010    2010      Yes
Chile     2002    2017      No
Mexico    2015    2010      Yes
          (IPUMS intercensal survey)
Argentina 2010    2010      No
Colombia  2005    2018      Yes


Reading in the sampling data and making necessary updates.

Here, we are using the IPUMS data; in Brazil there was an issue so we had to use only harmonized variables...

```{r}
census<- read.csv(
  paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/',country,'/sample/',country,'_ipums-census_geo.csv') #'ipumsi_00023.csv')#
  )
```
```{r}
netquest <- read.csv(
  paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",
  country,
  "/panel/", country, "_netquest-panel_geo.csv")
)
```



```{r}
save.image(paste0(country,"_data_loaded.RData"))
```

```{r}
#load(paste0(country,"_data_loaded.RData"))
```


We have to recode the various characteristics we have at our disposal.
```{r}
matching.vars <- c('gend', 
                   'age', 
                   'ed', 
                   #'ed_hhh', 
                   'emp', 
                   #'emp_hhh', 
                   #'san', 
                   'auto',
                   #'cell',
                   'nbath',
                   'pc',
                   'fridg',
                   #'motoc',
                   'washer',
                   #'insur_hhh', 
                   #'walls', 
                   #'floors', 
                   'child',
                   #'hhinc',
                   'radio',
                   'tv',
                   #'water',
                   'marst',
                   'pern',
                   'hhtype',
                   'hhh',
                   #'prov', using X and Y instead of province
                   'X',
                   'Y'
                   )
```

Gender:          is fine.
```{r}
census$gend <- census$SEX
netquest$gend <- netquest$p_sexo
```

```{r}
unique(netquest$gend)
```

Age:          is fine, need to filter these to make sure we exclude too young respondents.
```{r}
census$age <- mapvalues(census$AGE, from=c(999), to=c(NA))
netquest$age <- netquest$panelistAge
netquest$age[netquest$panelistAge>100] <- 100
```
```{r}
unique(netquest$age)
```


Education:    EDUCCL partially matches CL_education_level; the census doesn't count postgrad so have to collapse in panel

```{r}
census$ed <- rep(NA, length=length(census$EDUCBR))
census$ed[census$EDUCBR==0] <- 1
census$ed[census$EDUCBR>=1000 & census$EDUCBR<=2140] <- 2
census$ed[(census$EDUCBR==2141)|(census$EDUCBR==2190)] <- 3
census$ed[(census$EDUCBR>=2210 & census$EDUCBR<=2230)|census$EDUCBR==2900] <- 4
census$ed[(census$EDUCBR==2241)|(census$EDUCBR==2290)] <- 5
census$ed[census$EDUCBR>=3100 & census$EDUCBR<=3200] <- 6
census$ed[census$EDUCBR %in% c(3300, 3900)] <- 7
census$ed[census$EDUCBR %in% c(4170, 4180)] <- 8
census$ed[census$EDUCBR==4190] <- 9
census$ed[census$EDUCBR %in% c(4270, 4280)] <- 10
census$ed[census$EDUCBR %in% c(4230, 4240)] <- 11
census$ed[census$EDUCBR %in% c(4250, 4260)] <- 12

netquest$ed <- as.integer(netquest$BR_education_level_full)
```

    Need head of household, as well--HHH INFORMATION NOT AVAILABLE IN BRAZIL!

Employment. Reconsider ordering.
```{r}
census$emp <- mapvalues(census$EMPSTAT,
        from=c(1, 2, 3,  0),
        to=  c(1, 3, 4, NA))
census$emp[census$CLASSWK==2]<- 2   # Wage/salary worker
netquest$emp <- mapvalues(netquest$BR_laboral_situation,
       from=c(1,2,3,4,5,6,7,8,9),
       to=  c(2,1,4,3,4,3,4,4,4))
```
```{r}
unique(census$emp)
```

  Employment of head of household: no HHH in Brazil


Auto
```{r}
census$auto <- mapvalues(census$AUTOS,
        from=c(0,7,9),
        to=  c(2,1,NA))
netquest$auto <- mapvalues(netquest$BR_numAutos,
       from=c(1,2,3,4,5),
       to=  c(2,1,1,1,1))
unique(netquest$auto)
```


Have bathroom?
```{r}
census$nbath <- mapvalues(census$BATH,
        from=c(1,2,0),
        to=  c(2,1,NA))
netquest$nbath <- mapvalues(netquest$BR_numBaths,
       from=c(1,2,3,4,5),
       to=  c(2,1,1,1,1))
unique(netquest$nbath)
```

Computer?
```{r}
census$pc <- mapvalues(census$COMPUTER,
                       from=c(1,2,0),
                       to  =c(2,1,NA)
                       )
netquest$pc <- mapvalues(netquest$BR_numComputer,
                         from=c(1,2,3,4,5),
                         to  =c(2,1,1,1,1)
                         )
unique(netquest$pc)
```

Fridge?
```{r}
census$fridg <- mapvalues(census$REFRIG,
                       from=c(1,2,0),
                       to  =c(2,1,NA)
                       )
netquest$fridg <- mapvalues(netquest$BR_numFridge,
                         from=c(1,2,3,4,5),
                         to  =c(2,1,1,1,1)
                         )
unique(netquest$fridg)
```


Washing machine?
```{r}
census$washer <- mapvalues(census$WASHER,
                       from=c(1,2,0),
                       to  =c(2,1,NA)
                       )
netquest$washer <- mapvalues(netquest$BR_numWashmachine,
                         from=c(1,2,3,4,5),
                         to  =c(2,1,1,1,1)
                         )
unique(netquest$washer)
```

Children
```{r}
census$child<-census$NCHILD
census$child[census$NCHILD>7] <- 7

netquest$child <- netquest$number_P3
netquest$child[netquest$P3==2] <- 0

unique(netquest$child)
```


Marital status: need P1 from Netquest!
```{r}
census$marst <- mapvalues(census$MARST,
                          from=c(1,2,3,4),
                          to  =c(1,4,2,3)
                          )

netquest$marst <- mapvalues(netquest$P1,
                          from=c(1,2,3,4),
                          to  =c(1,4,2,3)
                          )
unique(census$marst)
```

Has radio
```{r}
census$radio <- mapvalues(census$RADIO,
                       from=c(1,2,0),
                       to  =c(2,1,NA)
                       )
netquest$radio <- mapvalues(netquest$BR_2012_numRadio,
                         from=c(1,2,3,4,5),
                         to  =c(2,1,1,1,1)
                         )
unique(netquest$radio)
```

Has TV

```{r}
census$tv <- mapvalues(census$TV,
                       from=c(10,20,0),
                       to  =c(2,1,NA)
                       )
netquest$tv <- mapvalues(netquest$BR_2012_numTV,
                         from=c(1,2,3,4,5),
                         to  =c(2,1,1,1,1)
                         )

unique(netquest$tv)
```


number of persons in household
```{r}
census$pern <- census$PERSONS
netquest$pern <- netquest$P2
table(netquest$pern)
```

type of household
```{r}
census$hhtype <- mapvalues(census$HHTYPE,
                          from=c(1,5,6,7,8,2,3,4,6,11,99, 0),
                          to  =c(1,5,5,6,6,2,4,3,5, 0, 0,NA)
                          )

netquest$hhtype <- mapvalues(netquest$P8,
                          from=c(1,2,3,4,5,6,7,99),
                          to  =c(1,5,6,2,4,3,5, 0)
                          )
table(census$hhtype)
```
head of household?
```{r}
census$hhh <- vector(length=length(census$RELATE))
census$hhh[census$RELATE>1] <- 2
census$hhh[census$RELATE==1] <- 1

netquest$hhh <- mapvalues(netquest$P12,
                          from=c(1,2,3),
                          to  =c(1,2,1)
                          )

```

```{r}
hist(netquest$hhh)
```

Give ID to both datasets, so we can go back to IDs when necessary
```{r}
census$id <- seq(dim(census)[1])
netquest$id <- seq(dim(netquest)[1])
```


Create the sample and panel from this:


If we do some non-numeric matching, we'd want to adjust the labels/levels.
```{r}
panel <- to_factor(netquest[append(matching.vars, c('id'))],
                   drop_unused_labels = TRUE)

panel['Fakeid'] <- netquest[[NQ_id]]
panel <- panel[panel$age>17,]

panel <- na.omit(panel)        
summary(panel)
```


ADJUST FOR COUNTRY!
```{r}
census.proc <- to_factor(census[append(matching.vars,c(
  strat2,
  'PERWT',
  strat1,'id'))], drop_unused_labels = TRUE)

census.proc <- census.proc[census.proc$age>17,]

census.proc <- na.omit(census.proc)
census.proc <- census.proc[order(census.proc[strat1],census.proc[strat2]),]

summary(census.proc)
```

sample! Stratified by urban/rural and by region, weighted
!REMEMBER TO MATCH THE SEED!

```{r}
n <- 1200
set.seed(111)
strats=c(strat1,strat2)
library(sampleMatch)
target  <- strat_weight_sample(census.proc,strats,'PERWT',n)
#add Fakeid, so we can keep those from the panel in the matching set
target['Fakeid'] <- as.integer(rep(999999, length(target$age)))
```


Making sure this stratification worked...
```{r}
barplot(table(census.proc[[strat2]], census.proc[[strat1]]))
```




Add a treatment into it:
```{r}
panel['treat'] <- rep(0,length(panel$age))
target['treat'] <- rep(1,length(target$age))
```


Now join this data together:
```{r}
levels(panel$Fakeid) <- c(levels(panel$Fakeid),999999) #to make room for the non-existent Fakeid
alldata<-rbind(panel,target[names(panel)])


#jointId will be the sequence number in the joint dataframe -- MAY NOT NEED THIS?
alldata$jointId <- seq(dim(alldata)[1])
rownames(alldata) <- alldata$jointId


unique(table(alldata$id))
```
Divide target sample into age quantiles (in this case, deciles) and add that to the data:
```{r}
age_q <- quantile(target$age,prob = seq(0,1,0.1))
alldata['age_group'] <- as.integer(cut(alldata$age,breaks = age_q, include.lowest = TRUE))
alldata$age_group[is.na(alldata$age_group)] <- 10
```

#for the methods that require numeric approximation
```{r}
alldata_num<-data.frame(lapply(alldata, as.numeric))
```

```{r}
summary(alldata_num)
```





Now the matching begins. This is using the MatchIt package as we are used to...
```{r}

matching.form <- as.formula(paste0("treat ~ ", paste(matching.vars, collapse=' + ')))
```

We'll have to repeat this process (at least for everything except PS), since the memory can't deal with all of this. 
* start empty dataframe initialized with target IDs
* make a copy of the data to alter
* for each i in range:
  + run the matching
  + store the matched IDs
  + store some overall metrics about the match
  + reduce the panel data
* return the match objects

```{r}
matchRatio <- function(data, metric, n, exact = c()){
  
  # assign the dataframe to hold the matching results
  df <- data.frame(matrix(ncol=1, nrow=sum(data$treat==1)))
  names(df) <- c("targetId")
  df$targetId <- data$id[data$treat==1]
  
  # assign the object to hold all the matching information
  matches <- vector("list",n)
  
  # make a copy of the passed-in data
  data.copy <- data.frame(data)
  
  
  # loop over the number of respondents per target
  # if there are issues, can I relax the age groups?
  for(i in 1:n){
    print(paste('i = ',to_character(i)))
    m <- matchit(matching.form, 
                 data = data.copy, exact=exact, method = "nearest", distance = metric)
    
    try({matches[[i]] <- m
        targetids <- data.copy[row.names(m$match.matrix), "id"]
        panelids <- as.data.frame(data.copy[m$match.matrix,"Fakeid"])
        names(panelids)<-c("panelId")
        panelids['targetId']<-targetids
        df <- merge(x=df, y=panelids, by="targetId", all.x = TRUE, suffixes=c("",to_character(i)))
        } #... maybe merge instead might be safer?
    )
    
    controls <- match.data(m, group='control')
    data.copy <- data.copy[!data.copy$jointId %in% controls$jointId,] # not relying on rownames
    
  }
  return(list("ids"=df, "matches"=matches))
}

```

```{r}
matches.cem_mah = matchRatio(alldata_num, "mahalanobis", 1, exact = c("age_group","gend"))
```


Save the id's of the matches to a file, so I don't lose them--just in case
```{r}
tmp <- matches.cem_mah$ids

# attaching NQ panel code
tmp[NQ_id] <- merge(x = matches.cem_mah$ids, 
                    y = alldata[alldata$treat==0, c("Fakeid",'id')], 
                    by.x = "panelId", 
                    by.y = "id")[["Fakeid"]]

# attaching census identification, just in case!
tmp[c("SERIAL","PERNUM")] <- merge(x = matches.cem_mah$ids,
                                   y = census[c("SERIAL","PERNUM","id")],
                                   by.x = 'targetId',
                                   by.y = 'id')[c("SERIAL","PERNUM")]

write.csv(x=tmp[c("targetId",NQ_id, "SERIAL","PERNUM")], file=paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country,"/panel/matches_cem-mah.csv"))
```
```{r}
summary(tmp)
```







