---
title: "sample-matching_IPUMS-NQ_BR"
author: "Maita Schade"
date: "May 17, 2019"
output: html_notebook
---


run: *Ctrl+Shift+Enter*. 
New chunk: *Ctrl+Alt+I*.
*Ctrl+Shift+K* to preview the HTML file.

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```

```{r}
country = "MX"
strat1 = "GEO1_MX2015"
strat2 = "URBAN"
NQ_id  = "gp_codigo"

setwd(
  paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country)
)
```


```{r}
library('MatchIt')
library('haven')
library('openxlsx')
library('labelled')
library(zoo)

require('cem')

require(plyr)

require(sampleMatch) #my personal special package for this project.

```

A word or two about feasibility. The only census information we can get is from IPUMS (it seems), and for the countries we are considering, these are the most recent:

country   IPUMS   census    weighted
Peru      2007    2017      No
Brazil    2010    2010      Yes
Chile     2002    2017      No
Mexico    2015    2010      Yes
          (IPUMS intercensal survey)
Argentina 2010    2010      No
Colombia  2005    2018      Yes

Reading in the sampling data and making necessary updates.

Here, we are using the IPUMS data.
```{r}
census<- read.csv(
  paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/',country,'/sample/',country,'_ipums-census_geo.csv')
  )
```

```{r}
netquest <- read.csv(
  paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",
  country,
  "/panel/", country, "_netquest-panel_geo.csv")
)

netquest<-netquest[!duplicated(netquest[NQ_id]),]
```

```{r}
save.image(paste0(country,"_data_loaded.RData"))
```

```{r}
#load(paste0(country,"_data_loaded.RData"))
```



We have to recode the various characteristics we have at our disposal.
```{r}
matching.vars <- c('gend', 
                   'age', 
                   'ed', 
                   'ed_hhh', 
                   'emp', 
                   'emp_hhh', 
                   #'san', 
                   'auto',
                   #'cell',
                   #'nbath',
                   'pc',
                   'web',
                   'lightbulb',
                   # 'fridg',
                   # 'motoc',
                   # 'washer',
                   #'insur_hhh', 
                   #'walls', 
                   'floors', 
                   'nrooms',
                   #'nbr',
                   'shower',
                   'tv',
                   'child',
                   # 'hhinc',
                   # 'radio',
                   # 'water',
                   'marst',
                   'pern',
                   'hhtype',
                   'hhh',
                   #'prov', using X and Y instead of province
                   'X',
                   'Y'
                   )
```

Gender:          is fine.
```{r}
census$gend <- census$SEX
netquest$gend <- netquest$p_sexo
```
```{r}
unique(census$gend)
```

Age:          is fine, need to filter these to make sure we exclude too young respondents.
```{r}
census$age <- mapvalues(census$AGE, from=c(999), to=c(NA))
netquest$age <- netquest$panelistAge
netquest$age[netquest$panelistAge>100] <- 100
```
```{r}
sort(unique(netquest$age))
```


Education:    

```{r}
census$ed <- rep(NA,length=length(census$EDUCMX))
census$ed[census$EDUCMX== 10] <- 1
census$ed[census$EDUCMX>= 20 & census$EDUCMX<= 29] <- 2
census$ed[census$EDUCMX>=100 & census$EDUCMX<=109] <- 3
census$ed[census$MX2015A_EDLEVEL==2] <- 4
census$ed[census$EDUCMX>=200 & census$EDUCMX<=229] <- 5
census$ed[census$MX2015A_EDLEVEL==3] <- 6
census$ed[census$MX2015A_EDLEVEL%in%c(6,7,8,9)] <- 7
census$ed[census$EDUCMX>=300 & census$EDUCMX<=339] <- 8
census$ed[census$MX2015A_EDLEVEL%in%c(4,5)] <- 9
census$ed[census$EDUCMX>=610 & census$EDUCMX<=619] <- 10
census$ed[census$MX2015A_EDLEVEL%in%c(10,11)] <- 11
census$ed[census$MX2015A_EDLEVEL%in%c(12,13)] <- 12
census$ed[census$MX2015A_EDLEVEL==14] <- 13
#census$ed[census$EDUCMX==999|census$EDUCMX==800] <- NA


netquest$ed <- mapvalues(netquest$MX_education_level_merge,
                         from=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14),
                         to  =c(1,2,3,4,5,6,7,7,8, 9,10,11,12,13)
                         )
```
```{r}
print(sum(census$EDUCMX==800 | census$EDUCMX==999))
print(summary(census$ed))
```


Need head of household, as well

```{r}
census$ed_hhh <- rep(NA,length=length(census$EDUCMX_HEAD))
census$ed_hhh[census$EDUCMX_HEAD== 10] <- 1
census$ed_hhh[census$EDUCMX_HEAD>= 20 & census$EDUCMX_HEAD<= 29] <- 2
census$ed_hhh[census$EDUCMX_HEAD>=100 & census$EDUCMX_HEAD<=109 & census$MX2015A_EDLEVEL_HEAD<2] <- 3
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD==2] <- 4
census$ed_hhh[census$EDUCMX_HEAD>=200 & census$EDUCMX_HEAD<=229 & census$MX2015A_EDLEVEL_HEAD< 3] <- 5
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD==3] <- 6
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(6,7,8,9)] <- 7
census$ed_hhh[census$EDUCMX_HEAD>=300 & census$EDUCMX_HEAD<=339 & census$MX2015A_EDLEVEL_HEAD< 4] <- 8
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(4,5)] <- 9
census$ed_hhh[census$EDUCMX_HEAD>=610 & census$EDUCMX_HEAD<=619 & census$MX2015A_EDLEVEL_HEAD<10] <- 10
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(10,11)] <- 11
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD%in%c(12,13)] <- 12
census$ed_hhh[census$MX2015A_EDLEVEL_HEAD==14] <- 13
#census$ed_hhh[census$EDUCMX_HEAD==999|census$EDUCMX_HEAD==800] <- NA


netquest$ed_hhh <- mapvalues(netquest$MX_education_level_hhousehold_merge,
                         from=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14),
                         to  =c(1,2,3,4,5,6,7,7,8, 9,10,11,12,13)
                         )
```
```{r}
print(sum(census$EDUCMX_HEAD==800 | census$EDUCMX_HEAD==999))
print(summary(census$ed_hhh))
```

    

Employment. RECONSIDER ORDERING.
```{r}
census$emp <- rep(NA,length=length(census$EDUCMX_HEAD))
census$emp[census$MX2015A_EMPSTAT%in%c(10,12,16)] <- 1 
census$emp[census$MX2015A_CLASSWK%in%c(4,5)] <- 1     # Trabajo actualmente por cuenta propia
census$emp[census$MX2015A_EMPSTAT%in%c(11,13,14,15)] <- 3 
census$emp[census$MX2015A_CLASSWK%in%c(1,2,3)] <- 2   # Trabajo actualmente como empleado
census$emp[census$MX2015A_EMPSTAT== 31] <- 3          # Estudiante (sin trabajar)
census$emp[census$MX2015A_EMPSTAT== 20] <- 4          # Desempleado
census$emp[census$MX2015A_EMPSTAT== 32] <- 5          # Retirado/Pensionista
census$emp[census$MX2015A_EMPSTAT== 34] <- 6          # Incapacitado
census$emp[census$MX2015A_EMPSTAT== 33] <- 7          # Labores del hogar
census$emp[census$MX2015A_EMPSTAT== 35] <- 7          # Did not work--assume that means they did housework

netquest$emp <- mapvalues(netquest$MX_laboral_situation,
       from=c(1,2,3,4,5,6,7,8,9),
       to=  c(1,2,3,4,4,5,5,6,7))
```
```{r}
unique(census$emp)
```

  Employment of head of household: see above
```{r}
census$emp_hhh <- rep(NA,length=length(census$EDUCMX_HEAD))
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD%in%c(10,12,16)] <- 1 
census$emp_hhh[census$MX2015A_CLASSWK_HEAD%in%c(4,5)] <- 1     # Trabajo actualmente por cuenta propia
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD%in%c(11,13,14,15)] <- 3 
census$emp_hhh[census$MX2015A_CLASSWK_HEAD%in%c(1,2,3)] <- 2   # Trabajo actualmente como empleado
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 31] <- 3          # Estudiante (sin trabajar)
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 20] <- 4          # Desempleado
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 32] <- 5          # Retirado/Pensionista
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 34] <- 6          # Incapacitado
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 33] <- 7          # Labores del hogar
census$emp_hhh[census$MX2015A_EMPSTAT_HEAD== 35] <- 7          # Did not work--assume that means they did housework

netquest$emp_hhh <- mapvalues(netquest$MX_laboral_situation_hhousehold,
       from=c(1,2,3,4,5,6,7,8,9),
       to=  c(1,2,3,4,4,5,5,6,7))
```
```{r}
unique(census$emp_hhh)
```

Auto
```{r}
census$auto <- mapvalues(census$AUTOS,
        from=c(0,7,8,9),
        to=  c(2,1,NA,NA))
netquest$auto <- mapvalues(netquest$MX_NSE_cars,
       from=c(1,2,3,4),
       to=  c(2,1,1,1))
```
```{r}
unique(netquest$auto)
```



Computer?
```{r}
census$pc <- mapvalues(census$COMPUTER, 
                       from=c(0,1,2,9), 
                       to=c(NA,2,1,NA))
netquest$pc <- mapvalues(netquest$MX_NSE_computer,
                         from=c(1,2,3),
                         to  =c(2,1,1)
                         )
```
```{r}
unique(census$pc)
```

Internet?
```{r}
census$web <- mapvalues(census$INTERNET, from=c(0,1,2,9), to=c(NA,2,1,NA))
netquest$web <- mapvalues(netquest$MX_NSE_internet_at_home, from = c(1,2), to=c(1,2))
```
```{r}
summary(netquest$MX_NSE_internet_at_home)
```

Lightbulbs?
```{r}
census$lightbulb <- rep(NA,length=length(census$MX2015A_LIGHTBULB))
census$lightbulb[census$MX2015A_LIGHTBULB>= 0 & census$MX2015A_LIGHTBULB<= 5] <- 1
census$lightbulb[census$MX2015A_LIGHTBULB>= 6 & census$MX2015A_LIGHTBULB<=10] <- 2
census$lightbulb[census$MX2015A_LIGHTBULB>=11 & census$MX2015A_LIGHTBULB<=15] <- 3
census$lightbulb[census$MX2015A_LIGHTBULB>=16 & census$MX2015A_LIGHTBULB<=20] <- 4
census$lightbulb[census$MX2015A_LIGHTBULB>=21 & census$MX2015A_LIGHTBULB<=90] <- 5

netquest$lightbulb <- netquest$MX_NSE_lights
```
```{r}
unique(census$lightbulb)
```

Floors of dwelling (there is some ambiguity here between the vinilicos and laminadas de vinil)
PE_NSE_pavement	:
  1	Tierra / Otro material (arena y tablones sin pulir)
	2	Cemento sin pulir o pulido / Madera (entablados) / tapizón
	3	Losetas / terrazos, mayólicas, cerámicos, vinílicos, mosaico o similares
	3	Laminado tipo madera, láminas asfálticas o similares
	4	Parquet o madera pulida y similares; porcelanato,  alfombra, mármol

```{r}
#When going numeric, must replace NA with the average
census$floors <- mapvalues(census$MX2015A_FLOOR,
        from=c(1, 2, 3, 8, 9),
        to=  c(1, 1, 2,NA,NA))
netquest$floors <- mapvalues(netquest$MX_NSE_pavement,
        from=c(1, 2),
        to=  c(1, 2))
```
```{r}
unique(netquest$floors)
```

Number of rooms
```{r}
census$nrooms <- rep(NA,length=length(census$MX2015A_ROOMS))
census$nrooms[census$MX2015A_ROOMS<7] <- census$MX2015A_ROOMS[census$MX2015A_ROOMS<7]
census$nrooms[census$MX2015A_ROOMS>=7 & census$MX2015A_ROOMS<=20] <- 7 

netquest$nrooms <- netquest$MX_NSE_rooms
```

```{r}
unique(census$nrooms)
```
Shower?
```{r}
census$shower <- rep(NA,length=length(census$MX2015A_SHOWER))
census$shower[census$MX2015A_SHOWER<3] <-  census$MX2015A_SHOWER[census$MX2015A_SHOWER<3]

netquest$shower <- netquest$MX_NSE_shower
```

```{r}
unique(netquest$shower)
```
Number of TVs

```{r}
census$tv[census$MX2015A_TV%in%c(1,2)] <- census$MX2015A_TV[census$MX2015A_TV%in%c(1,2)]
netquest$tv <- mapvalues(netquest$MX_NSE_tv,
                         from=c(1,2,3,4),
                         to  =c(2,1,1,1)
                         )
```
```{r}
unique(census$tv)
```


Walls of dwelling
PE_NSE_walls:
  1	Estera
	2	Madera/ Piedra con barro/ Quincha (caña con barro)/ Tapia/ Adobe
	3	Piedra o sillar con cal o cemento
	4	Ladrillo o bloque de cemento


Children
```{r}
census$child<-rep(NA, length=length(census$NCHILD))
census$child[census$NCHILD<=7] <- census$NCHILD[census$NCHILD<=7]
census$child[census$NCHILD>7] <- 7

netquest$child <- netquest$number_P3
netquest$child[netquest$P3==2] <- 0
```
```{r}
unique(netquest$child)
```




Marital status: need P1 from Netquest!
```{r}
census$marst <- mapvalues(census$MARST,
                          from=c(1,2,3,4,9),
                          to  =c(1,4,2,3,NA)
                          )

netquest$marst <- mapvalues(netquest$P1,
                          from=c(1,2,3,4),
                          to  =c(1,4,2,3)
                          )
```
```{r}
unique(netquest$marst)
```




number of persons in household
```{r}
census$pern <- census$PERSONS
netquest$pern <- netquest$P2
```
```{r}
unique(census$pern)
```

type of household
```{r}
census$hhtype <- mapvalues(census$HHTYPE,
                          from=c(1,5,6,7,8,2,3,4,6,11,99, 0),
                          to  =c(1,5,5,6,6,2,4,3,5, 0, 0,NA)
                          )

netquest$hhtype <- mapvalues(netquest$P8,
                          from=c(1,2,3,4,5,6,7,99),
                          to  =c(1,5,6,2,4,3,5, 0)
                          )
```
head of household?
```{r}
census$hhh <- rep(NA,length=length(census$RELATE))
census$hhh[census$RELATE>1] <- 2
census$hhh[census$RELATE==1] <- 1

netquest$hhh <- mapvalues(netquest$P12,
                          from=c(1,2,3),
                          to  =c(1,2,1)
                          )
```

```{r}
hist(netquest$hhh)
```

Give ID to both datasets, so we can go back to IDs when necessary
```{r}
census$id <- seq(dim(census)[1])
netquest$id <- seq(dim(netquest)[1])
```


If we do some non-numeric matching, we'd want to adjust the labels/levels.
```{r}
panel <- to_factor(netquest[append(matching.vars, c('id'))],
                   drop_unused_labels = TRUE)

panel['Fakeid'] <- netquest[[NQ_id]]
panel <- panel[panel$age>17,]

panel <- na.omit(panel)        
summary(panel)
```

ADJUST FOR COUNTRY!
```{r}
census.proc <- to_factor(census[append(matching.vars,c(
  strat2,
  'PERWT',
  strat1,'id'))], drop_unused_labels = TRUE)
census.proc <- census.proc[census.proc$age>17,]

census.proc <- na.omit(census.proc)
census.proc <- census.proc[order(census.proc[strat1],census.proc[strat2]),]

summary(census.proc)
```

Try stratified sampling, with my custom package.

```{r}


n <- 1200
#require('sampling')
set.seed(111)
target  <- strat_weight_sample(census.proc,c(strat1,strat2),'PERWT',n)

#add Fakeid, so we can keep those from the panel in the matching set
target['Fakeid'] <- as.integer(rep(999999, length(target$age)))

```

Making sure this stratification worked...
```{r}
barplot(table(census.proc[[strat2]], census.proc[[strat1]]))
```

```{r}
barplot(table(target[[strat2]], target[[strat1]]))
```




Add a treatment into it:
```{r}
panel['treat'] <- rep(0,length(panel$age))
target['treat'] <- rep(1,length(target$age))
```


Now join this data together:
```{r}
alldata<-rbind(panel,target[names(panel)])

#jointId will be the sequence number in the joint dataframe -- MAY NOT NEED THIS?
alldata$jointId <- seq(dim(alldata)[1])
rownames(alldata) <- alldata$jointId


unique(table(alldata$id))


# add a level to the alldata fakeid to accommodate the target
levels(alldata$Fakeid) <- c(levels(alldata$Fakeid),999999)
alldata$Fakeid[is.na(alldata$Fakeid)]<-999999
```


Divide target sample into age quantiles (in this case, deciles) and add that to the data:
```{r}
age_q <- quantile(target$age,prob = seq(0,1,0.1))
alldata['age_group'] <- as.integer(cut(alldata$age,breaks = age_q, include.lowest = TRUE))
alldata$age_group[is.na(alldata$age_group)] <- 10
```

#for the methods that require numeric approximation
```{r}
alldata_num<-data.frame(lapply(alldata, as.numeric))
```

```{r}
summary(alldata_num)
```





Now the matching begins. This is using the MatchIt package as we are used to...
```{r}
matching.form <- as.formula(paste0("treat ~ ", paste(matching.vars, collapse=' + ')))
```

We'll have to repeat this process (at least for everything except PS), since the memory can't deal with all of this. 
* start empty dataframe initialized with target IDs
* make a copy of the data to alter
* for each i in range:
  + run the matching
  + store the matched IDs
  + store some overall metrics about the match
  + reduce the panel data
* return the match objects

```{r}
matchRatio <- function(data, metric, n, exact = c()){
  
  # assign the dataframe to hold the matching results
  df <- data.frame(matrix(ncol=1, nrow=sum(data$treat==1)))
  names(df) <- c("targetId")
  df$targetId <- data$id[data$treat==1]
  
  # assign the object to hold all the matching information
  matches <- vector("list",n)
  
  # make a copy of the passed-in data
  data.copy <- data.frame(data)
  
  
  # loop over the number of respondents per target
  # if there are issues, can I relax the age groups?
  for(i in 1:n){
    print(paste('i = ',to_character(i)))
    m <- matchit(matching.form, 
                 data = data.copy, exact=exact, method = "nearest", distance = metric)
    
    try({matches[[i]] <- m
        targetids <- data.copy[row.names(m$match.matrix), "id"]
        panelids <- as.data.frame(data.copy[m$match.matrix,"Fakeid"])
        names(panelids)<-c("panelId")
        panelids['targetId']<-targetids
        df <- merge(x=df, y=panelids, by="targetId", all.x = TRUE, suffixes=c("",to_character(i)))
        } #... maybe merge instead might be safer?
    )
    
    controls <- match.data(m, group='control')
    data.copy <- data.copy[!data.copy$jointId %in% controls$jointId,] # not relying on rownames
    
  }
  return(list("ids"=df, "matches"=matches))
}

```

```{r}
matches.cem_mah = matchRatio(alldata_num, "mahalanobis", 1, exact = c("age_group","gend"))
```
Save the id's of the matches to a file, so I don't lose them--just in case
```{r}
tmp <- matches.cem_mah$ids

# attaching NQ panel code
tmp[NQ_id] <- merge(x = matches.cem_mah$ids, 
                    y = alldata[alldata$treat==0, c("Fakeid",'id')], 
                    by.x = "panelId", 
                    by.y = "id")[["Fakeid"]]

# attaching census identification, just in case!
tmp[c("SERIAL","PERNUM")] <- merge(x = matches.cem_mah$ids,
                                   y = census[c("SERIAL","PERNUM","id")],
                                   by.x = 'targetId',
                                   by.y = 'id')[c("SERIAL","PERNUM")]

write.csv(x=tmp[c("targetId",NQ_id, "SERIAL","PERNUM")], file=paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/",country,"/panel/matches_cem-mah.csv"))
```
```{r}
summary(tmp)
```







