---
title: "recode (remedial Argentina)"
author: "Maita Schade"
date: "Sep 8, 2019"
output: html_notebook
---

This notebook helps in recoding panel and census datasets to a compatible format.
Important input that need to be adjusted with country specifics:
  * recode_Netquest_IPUMS_COUNTRY.csv currently supplies matching variables
  * country_parameters.csv supplies parameters (such as specific labels or strata)
  * recode_country.R contains the individual recodes for each country


Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```

Setting specifics--may want to iterate over countries rather than set things individually, eventually.
```{r}
country = "AR"
```

Defining files--make sure the dirs are okay; other than that you shouldn't need to touch this if the file structure is set up properly.
```{r}
datadir <-  paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/',country,'/')

censuspath <- paste0(datadir,'sample/',country,'_ipums-census_geo.csv')

netquestpath <- paste0(datadir, "panel/", country, "_netquest-panel_geo.csv")

recodepath <- paste0("./recode_Netquest_IPUMS_",country, ".csv") #table specifying recodes
parampath <- "./country_parameters.csv" # set specific parameters in this file
```



```{r}
library(data.table)
library(bit64)
```

Load country-specific parameters:
```{r}
params <- fread(parampath,key = "country")[country,]
NQ_id <- params$NQ_id
strats <- unlist(Filter(f = Negate(is.na), params[,c("strat1","strat2")]))
```

```{r}
recode_map <- fread(recodepath)
```


We have to recode the various characteristics we have at our disposal.
```{r}
matching.vars <- unique(recode_map$common_var)
```

Load external function to do the dirty work, depending on country etc.
Note that this function will need to get updated when adding new countries/data sources.
```{r}
source("./recode_country.R")
```




## Recode IPUMS

Load datafile
```{r}
print(censuspath)
census<- fread(censuspath)
```
```{r}
dim(census)
```

Recode
```{r}
census.proc <- countryRecode(dt = census, source = 'ipums', country = country)
```

```{r}
summary(census.proc)
```


Investigate ones with lots of NA:
```{r}
table(census$EMPSTAT)
```
These are not in universe.
```{r}
table(census$AR2010A_EDLEV)
```
This is special ed, and not in universe.


Give ID to all members
```{r}
census.proc$censusId <- paste0(
  sprintf(
    paste0('%0',
           as.character(max(nchar(census.proc$SERIAL))),
           '.0f'),
    census.proc$SERIAL),
  sprintf(
    paste0('%0',
           as.character(max(nchar(census.proc$PERNUM))),
           '.0f'),
    census.proc$PERNUM)
)
max(table(census.proc$censusId)) #make sure is unique!
census.proc$censusId[1:10]
table(nchar(census$SERIAL))
```

Then cut things down
```{r}
#census.proc <- census.proc[,,with=F
#                           ]
census.proc <- census.proc[census.proc$age>17,]
census.proc <- census.proc[,c('censusId','PERWT',matching.vars,strats[strats!=""]),with=F]
census.proc <- na.omit(census.proc)
head(census.proc)

summary(census.proc)
```
```{r}
dim(census.proc)
```

Save to disk:
```{r}
write.csv(x = census.proc, 
          file = paste0(datadir,'/sample/', country,'_ipums_recoded.csv'),
          row.names = F
)
```



## Recode Netquest

Load datafile
```{r}
netquest <- fread(netquestpath)
sort(unique(netquest$X))
```

Recode
```{r}
netquest.proc <- countryRecode(dt = netquest, source = 'netquest', country = country)
summary(netquest.proc)
```
Reduce to what we need:

```{r}
netquest.proc$panelId  <- netquest.proc[[NQ_id]]
netquest.proc <- netquest.proc[netquest.proc$age>17,]
netquest.proc <- netquest.proc[,c(matching.vars, 'panelId'),with=F]
head(netquest.proc)
netquest.proc <- na.omit(netquest.proc)        
summary(netquest.proc)
```

Save to disk:
```{r}
write.csv(x = netquest.proc, 
          file = paste0(datadir,'/panel/', country, '_netquest_recoded.csv'),
          row.names = F
)

```

