---
title: "sample (IDB Trust)"
author: "Maita Schade"
date: "Aug 8, 2019"
output: html_notebook
---

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```
  
Set the following chunk depending on the circumstances:
```{r}
country = "BR"
```

Defining files--make sure the dirs are okay; other than that you shouldn't need to touch this if the file structure is set up properly.
```{r}
rawdir <- paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online Trust/raw/')
datadir = paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online Trust/prep/out/')

censuspath <- paste0(datadir,'ipums_country/', country,'_ipums_recoded.csv')

varpath <- paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online Trust/doc/matching/matching_vars.csv")
parampath <- "./country_parameters.csv" # set specific parametrs in this file
```

```{r}
library(data.table)
library(devtools)
#install.packages('devtools')
#install_github("maitagorri/sampleMatch")
library(sampleMatch)
```

Load country-specific parameters:
```{r}
params <- fread(parampath,key = "country",na.strings = "")[country,]
strats <- unlist(Filter(f = Negate(is.na), params[,c("strat1","strat2")]))
```


Reading in the sampling data and making necessary updates.

Here, we are using the IPUMS data.
```{r}
census<- fread(censuspath, colClasses = c(censusId="character")) #keep it simple, and keep leading 0s
head(census)
```

Define the sampling function
```{r}
strat_weight_sample <- function(df, strats, weights, N){
  census <- df

  #First, we'll make a table of strata, and their sum of weights.
  blocks <- aggregate(as.formula(paste0(weights, " ~ ", paste(strats, collapse=' + '))), data=census, sum)
  print(as.formula(paste0(weights, " ~ ", paste(strats, collapse=' + '))))

  #Then we determine how many individuals to randomly draw from each stratum.
  blocks$nblock <- round(blocks[[weights]] * N/sum(blocks[[weights]]))

  #Then we do a weighted random sample from each stratum.
  weighted_sample_helper <- function(r){
    s1 <- r[[strats[1]]]
    if (length(strats)>1){
      s2 <- r[[strats[2]]]
      block <- census[(census[strats[1]]==s1) & (census[strats[2]]==s2),]
    }
    else{
      block <- census[(census[strats[1]]==s1),]
    }
    # block <- merge(t(r[strats]), census, by=c('URBAN','GEO1_CO2005'))
    n = as.double(r['nblock'])
    index = sample(nrow(block),
                   size = n,
                   replace = TRUE,
                   prob = block[[weights]]
    )
    return(block[index,])
  }

  #...and bind them together
  sample <- do.call(rbind, apply(blocks,1,weighted_sample_helper))
  return(sample)
}
strats
```



Try stratified sampling.

```{r}
n <- 1200
set.seed(191010)
target  <- strat_weight_sample(census,strats,'PERWT',n)
dim(target)
```


Making sure this stratification worked...
```{r}
barplot(table(target[[strats[1]]]))
barplot(table(census[[strats[1]]]))
nrow(target)
head(target)
hist(target$ed, xlim = c(1,6))
hist(census$ed)
table(target$age,target$gend)
```

Add a sample id, counting those that occur more than once:
```{r}
target$SAMPCT<-1
multis <- unique(target[duplicated(target$censusId),'censusId'])

for (i in multis){
  print(i)
  target[target$censusId==i,'SAMPCT':=1:table(target$censusId)[i]]
}
table(target$SAMPCT) # check that the sampcounts are right

target$sampleId <- paste0(
  target$censusId,
  sprintf(
    paste0('%0',
           as.character(max(nchar(target$SAMPCT))),
           '.0f'),
    target$SAMPCT)
)
head(target)
```


Dice just the variables needed for matching
```{r}
recode_map <- fread(recodepath)
matching.vars <- unique(recode_map$common_var)
target <- target[,c("sampleId",matching.vars),with=F]
```

Write target to disk.
```{r}
names(target)
write.csv(x=target,
          file = paste0(datadir,
                        "sample/",
                        country,
                        "_target_",
                        format(Sys.time(),
                        "%y%m%d"),
                        ".csv"),
          row.names = F
                    )

```
