---
title: "sample (IDB Trust)"
author: "Maita Schade"
date: "Aug 8, 2019"
output: html_notebook
---

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```
  
Set the following chunk depending on the circumstances:
```{r}
countries = c("AR","BR","CL","CO","MX","PE")
n = 1200 #sample size in each country
```

Defining files--make sure the dirs are okay; other than that you shouldn't need to touch this if the file structure is set up properly.
```{r}
rawdir <- paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online Trust/raw/')
datadir = paste0('C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online Trust/prep/out/')

varpath <- paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online Trust/doc/matching/matching_vars.csv")
parampath <- "C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online Trust/prep/src/country_parameters.csv" # set specific parameters in this file
```

```{r}
library(data.table)
library(devtools)
```
Add region variables for stratifying

Define the sampling function
```{r}
strat_weight_sample <- function(df, strats, weights, N){
  census <- df

  #First, we'll make a table of strata, and their sum of weights.
  blocks <- aggregate(as.formula(paste0(weights, " ~ ", paste(strats, collapse=' + '))), data=census, sum)
  print(as.formula(paste0(weights, " ~ ", paste(strats, collapse=' + '))))

  #Then we determine how many individuals to randomly draw from each stratum.
  blocks$nblock <- round(blocks[[weights]] * N/sum(blocks[[weights]]))
    # Use "ceiling" for always rounding up / larger N

  #Then we do a weighted random sample from each stratum.
  weighted_sample_helper <- function(r){
    s1 <- r[[strats[1]]]
    if (length(strats)>1){
      s2 <- r[[strats[2]]]
      block <- census[(census[[strats[1]]]==s1) & (census[[strats[2]]]==s2),]
    } else{
      block <- census[(census[[strats[1]]]==s1),]
    }
    # block <- merge(t(r[strats]), census, by=c('URBAN','GEO1_CO2005'))
    n = as.double(r['nblock'])
    index = sample(nrow(block),
                   size = n,
                   replace = TRUE,
                   prob = block[[weights]]
    )
    return(block[index,])
  }

  #...and bind them together
  # result <-data.table()
  # print(nrow(result))
  # while (nrow(result)<N){
    result <- do.call(rbind, apply(blocks,1,weighted_sample_helper))
  # }
  return(result)
}

```

Loop over countries:
```{r}
for (country in countries){
  #Load/set country-specific parameters:
  
  censuspath <- paste0(datadir,'ipums_country/', country,'_ipums_recoded.csv')
  params <- fread(parampath,key = "country",na.strings = "")[country,]
  strats <- unlist(Filter(f = Negate(is.na), params[,c("strat1","strat2")]))

  #Reading in the sampling data and making necessary updates.
  
  #Here, we are using the IPUMS data.
  census<- fread(censuspath, colClasses = c(censusId="character")) #keep it simple, and keep leading 0s
  print(paste0("strata for ",country, ": ", paste(strats,collapse = ", ")))

  #Try stratified sampling.
  #set.seed(191010) Should I set a seed?
  target  <- strat_weight_sample(census,strats,'PERWT',n)
  print(paste0("Final target size in ",country,": ",nrow(target)))

  #Add a sample id, counting those that occur more than once (this is possible since we're sampling with replacement, but shouldn't occur too often):
  target[,SAMPCT:=1]
  target[,SAMPCT:=as.integer(SAMPCT)]
  multis <- unique(target[duplicated(censusId)][['censusId']])
  for (i in multis){
    # print(i)
    target[censusId==i,'SAMPCT':=1:table(target$censusId)[i]]
  }
  table(target$SAMPCT) # check that the sampcounts are right

  target$sampleId <- paste0(
    target$censusId,
    sprintf(
      paste0('%0',
             as.character(max(nchar(target$SAMPCT))),
             '.0f'),
      target$SAMPCT)
  )

  #Dice just the variables needed for matching
  matching.vars <- grep(".",fread(varpath)[[country]],value = T) #grab variables that are not the empty string
  target <- target[,c("sampleId",matching.vars),with=F]
  
  # Write target to disk.
  print(
    paste("Writing these variables to target: ",
           paste(names(target), collapse = ", ")
    )
  )
  write.csv(x=target,
            file = paste0(datadir,
                          "sample/",
                          country,
                          "_target_",
                          format(Sys.time(),
                          "%y%m%d"),
                          ".csv"),
            row.names = F
                      )
  }

```

# Stuff for checking

Making sure this stratification worked...
```{r}
barplot(table(target[[strats[1]]]))
barplot(table(census[[strats[1]]]))
nrow(target)
head(target)
hist(target$ed, xlim = c(1,6))
hist(census$ed)
table(target$age,target$gend)
```

