---
title: "sample-matching_IPUMS-NQ_BR"
author: "Maita Schade"
date: "May 13, 2019"
output: html_notebook
---


run: *Ctrl+Shift+Enter*. 
New chunk: *Ctrl+Alt+I*.
*Ctrl+Shift+K* to preview the HTML file.

Make sure we're dealing with a clear space:
```{r}
rm(list = ls(all = TRUE))
```

```{r}

wd<-paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Matching process/Data/")
```


```{r}
library('haven')
library('openxlsx')
require(plyr)
require(reshape2)
require(stringr)
require(ggplot2)


```
```{r}
completedate = "190801"
```

```{r}
countries <- vector(mode='list', length=5)
names(countries) <- c("AR","BR","CL","CO","MX")

for (country in names(countries)){
  countries[[country]] <- vector(mode='list',length=5)
  names(countries[[country]]) <- c('name','NQ_id','target','selected','responded')
  countries[[country]][['name']] <- country
  if (!country=='AR'){countries[[country]]$'NQ_id' <- 'gp_codigo'} else {countries[[country]]$'NQ_id' <- 'p_codigo'}
}
```

  
  
```{r}
for (country in names(countries)){
# Setting variables we will be using for this country
  NQ_id <- countries[[country]]$NQ_id
# Printing what invites are considered
  cat("****************************************************************************************************\n")
  cat(paste0("Included invite files for ",country,": \n"))
  
# Reading in invite files from all waves
  waves <- lapply(list.files(path=paste0(wd,country,"/panel/"), pattern = "wave"), function (x){
    cat(paste0("    ",x,"\n"))
  ## We make sure the individual waves have distinguishable names by attaching suffixes
    
    df<-read.csv(paste0(wd, country, "/panel/",x),as.is = T) #c(NQ_id,"SERIAL","PERNUM"))
    df[names(df)[grep(NQ_id,names(df))]]<-sapply(df[names(df)[grep(NQ_id,names(df))]], tolower)
    nwave=as.numeric(str_match(x, "wave(\\d+)")[2])
    suffix=paste0(".",nwave+0:(ncol(df)-5))
    names(df)[grep(NQ_id,names(df))] <- paste0(NQ_id,suffix)
    return(df)
   }
  )
  
  # Creating a single distinguishable sample ID for each individual target record
  waves <- lapply(waves,function(x){
    x$SAMPCT <- rep(1, nrow(x))
    x$SAMPID <- paste0(
      sprintf('%010.0f',x$SERIAL),
      sprintf('%03.0f',x$PERNUM)
    )
    
  ## Individual person records that were drawn multiple times due to weighting will have a higher sample count
    for (i in unique(x[duplicated(x$SAMPID),'SAMPID'])){
      x[x$SAMPID==i,'SAMPCT']<- 1:length(x[x$SAMPID==i,'SAMPCT'])
      }
    return(x)
    }
  )
  
  # The target is a table of target records, with selected panelist IDs for each wave
  target <- Reduce(function(dtf1, dtf2) {merge(dtf1,#[-grep("X|targetId",names(dtf1))], 
                                               dtf2[-grep("X|targetId",names(dtf2))], 
                                               by = c("SAMPID","SAMPCT","SERIAL","PERNUM"), 
                                               all.x = TRUE)},
                   waves)
  target <- target[names(target)[-grep("targetId|X",names(target))]]

  cat('\t"selected" is a long list of all NQ panelists selected from our end\n')
  selected_wide <- Reduce(function(dtf1, dtf2) {merge(dtf1, dtf2[-grep("X|targetId",names(dtf2))], 
                                               by = c("SAMPID","SAMPCT","SERIAL","PERNUM"), 
                                               all.x = TRUE, all.y = TRUE)},
                   waves)
  selected <- selected_wide[names(selected_wide)[-grep("targetId|X",names(selected_wide))]]
  selected <- melt(data = selected,measure.vars = c(grep(NQ_id,names(selected))))
  names(selected)<-c("SAMPID",   "SAMPCT",   "SERIAL",   "PERNUM",   "variable", NQ_id)
  selected<-selected[!is.na(selected[[NQ_id]]),]
  selected$wave <- as.integer(regmatches(selected$variable, 
                                         regexpr("\\.\\K\\d+$",selected$variable,perl=TRUE)
                                         )
                              )
  
  # "responded" are just all the IDs NQ has recorded responding to our survey
  cat(paste0("Included response files for ",country,": \n"))
  responded <- lapply(list.files(path=paste0(wd,country,"/panel/"), pattern = "complete_\\d*\\.xlsx$"), function (x){
    cat(paste0("    ",x,"\n"))
    df<-read.xlsx(paste0(wd, country, "/panel/",x))
    names(df)[1] <- NQ_id
    return(df)
   }
  )
  names(responded)<-lapply(list.files(path=paste0(wd,country,"/panel/"), pattern = "complete_\\d*\\.xlsx$"), 
           function(s){str_match(s,"complete_(\\d\\d\\d\\d\\d\\d)")[2]})
  
  

  
  # ... for identifying how many targets have been hit, attach to each respondent its unique SAMPID
  resp_detail <- lapply(responded, function(df){join(x=df,y=selected, by=NQ_id)})
  resp_detail <- lapply(resp_detail, function(df){
    ID <- paste0(df$SAMPID, df$SAMPCT)
    df <- df[!is.na(ID),]
    ID <- ID[!is.na(ID)]
    return(cbind(df,ID))
  })
  
# Updating selected by wiping out the unused gp_codigos here--
# --if someone responded, we don't invite for that SAMPID for the following waves
lapply(resp_detail, function(df){
                          if (10%in%df$wave){
                            apply(df[df$wave>=10&!is.na(df$wave),c(NQ_id,"SAMPID","wave")],1,
                                function(r){
                                  selected[selected$wave>as.integer(r[["wave"]]) & selected$SAMPID==r[["SAMPID"]],NQ_id] <- NA
                                  assign('selected',selected,pos=.GlobalEnv)
                                  return(invisible())
                                }
                            )
                          }
                        }
  )

# Accounting for intentional "duplicates" due to weights by counting each ID in target and responses:
  nsamp_resp <- lapply(resp_detail, function(df){table(df$SAMPID)}) 
  nsamp_targ <- table(target$SAMPID)
  
  dupes <- as.array(lapply(nsamp_resp, function(df){
    sum(sapply(names(df), function(x){
      if (df[x]>nsamp_targ[x]){
        df[x]-nsamp_targ[x]
        } 
      else {0}
      }))
  }))
  respcount <- as.array(mapply(function(a,b){a-b},lapply(responded,nrow),dupes))
  
  # cat(paste0("\nDuplicates in ", country, ": ", dupes,"\n"))
  # cat(paste0("Valid completes in ", country, ": ", respcount,"\n"))
  # cat(paste0("Number of selections in ", country, ": ", nrow(selected),"\n"))
  
# In case we need to do anything else for the countries, saving them in this lovely data structure
  countries[[country]][['target']] <- target
  countries[[country]][['selected']] <- selected
  countries[[country]][['waves']] <- waves
  countries[[country]][['responded']] <- resp_detail
  countries[[country]][['count']]<-respcount
  countries[[country]][['dupes']]<-dupes
}
```


Setting up special colors
```{r}
lapop.red <- rgb(255/255,27/255,34/255)
lapop.mustard <- rgb(241/255,182/255,16/255)
lapop.yellow <- rgb(245/255,205/255,0/255)
lapop.purple <- rgb(81/255,43/255,113/255)
lapop.orange <- rgb(235/255,145/255,27/255)
lapop.olive <- rgb(185/255,196/255,34/255)
lapop.green <- rgb(0/255,163/255,72/255)
lapop.turquoise <- rgb(0/255,161/255,176/255)
lapop.pal <- c(lapop.mustard,lapop.turquoise,lapop.purple,lapop.green,lapop.red,lapop.olive,lapop.orange,lapop.yellow)
palette(lapop.pal)
```

Valid response count
```{r}
tmp <- sapply(countries, function(df){df$count})
tmp$BR<-append(c(0), tmp$BR)
nvalid <- as.data.frame(tmp)
nvalid$Date <- rownames(nvalid)
nvalid.long <- melt(nvalid, value.name = "Responses",variable.name = "Country")
nvalid.long$Type <- "Valid"
```

Number of duplicates
```{r}
tmp <- lapply(countries, function(df){unlist(df$dupes)})
tmp$BR<-append(c(0), tmp$BR)
ndupes <- data.frame(tmp)
ndupes$Date <- rownames(ndupes)
ndupes.long <- melt(ndupes, value.name = "Responses",variable.name = "Country")
ndupes.long$Type <- "Duplicate"
```



```{r}
rcounts <- rbind(nvalid.long,ndupes.long)

ggplot(rcounts, aes(x=Date, y=Responses, fill=Type)) + geom_bar(stat="identity",width=0.8,position='stack',alpha=0.6) + facet_grid(~ Country) +
  geom_hline(yintercept = 1200,color=5,size=1) +
  scale_fill_manual(values=lapop.pal) +
  annotate("text", 2, 1200, vjust = 1, label = "Target", color=5) + 
  theme(axis.text.x = element_text(angle = 90))

ggsave(paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Admin/Reporting/resp_count.png"), width = 7, height = 4)
```

Number of selected panelists
```{r}
tmp <- lapply(countries, function(x){
  unlist(lapply(x$waves,nrow))
  }
  )
tmp$BR<-append(c(0),tmp$BR)

nselected <- data.frame(tmp,row.names = 1:length(waves))
totselected <- sapply(nselected, cumsum)
totselected.long <- melt(totselected, value.name="Invites", varnames = c("Wave","Country" ))
totselected.long
ggplot(data = totselected.long, aes(x=Wave, y=Invites, fill=Country)) +
  geom_bar(stat="identity",width=0.8,position='dodge',alpha=0.5) +
  scale_fill_manual(values=lapop.pal)  +
  geom_hline(yintercept = 1200,color=5,size=1) + 
  annotate("text", 1, 1200, vjust = -1, label = "Target", color=5) 
  
ggsave(paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Admin/Reporting/selection_count.png"), width = 7, height = 4)
```
WE DON'T KNOW ABOUT ACTUAL INVITES RIGHT NOW, SO THIS WILL HAVE TO WAIT

Most recent selected panelists:
```{r}
actual_invites = data.frame(AR=3436,BR=3944,CL=3974,CO=3263,MX=3632, row.names = c("190711"))
actual_invites['190715',]<- c(AR = 313, CO=227, CL=312, MX=220, BR=440)+actual_invites["190711",]
actual_invites$Date = row.names(actual_invites)
actual_invites = melt(actual_invites,variable.name = "Country",value.name = "Invites")
actual_invites$Type <- "Sent"
actual_invites
```



Invites versus actually sent versus response
```{r}
currentdate <- "190715"
currentwave <- length(waves)
curr.selected <- totselected.long[totselected.long$Wave==currentwave,]
curr.selected$Type <- "Selected"
invites <- rbind(curr.selected[c("Country","Type","Invites")],actual_invites[actual_invites$Date==currentdate,c("Country","Type","Invites")])

ggplot(data = invites, aes(x=Country, y=Invites, fill=Type))+
  geom_bar(stat="identity",width=0.8,position='identity',alpha=0.7) +
  scale_fill_manual(values=lapop.pal) 

ggsave(paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Admin/Reporting/invites_actual_selected.png"), width = 7, height = 4)
```


Invites versus actually sent versus response (only the valid right now)
```{r}
inv.resp <- rcounts[(rcounts$Date==currentdate)&(rcounts$Type=="Valid"),names(rcounts)[grep("Date",names(rcounts),invert = TRUE)]]
names(inv.resp)[names(inv.resp)=="Responses"]<-"Invites"
inv.resp$Type<-"Responded"

inv.resp <- rbind(invites,inv.resp)
inv.resp$Type <- factor(inv.resp$Type, levels = c("Selected","Sent","Responded"))
inv.resp$Rate[inv.resp$Type=="Responded"] <- inv.resp$Invites[inv.resp$Type=="Responded"]/inv.resp$Invites[inv.resp$Type=="Sent"]

ggplot(data = inv.resp, aes(x=Country, y=Invites, fill=Type))+
  geom_bar(stat="identity",width=0.8,position='identity',alpha=0.9) +
  scale_fill_manual(values=lapop.pal) +
  geom_text(aes(x=Country, y=Invites, label=ifelse(!is.na(Rate), paste0(sprintf("%0.1f", 100*Rate), "%"), "")), 
              vjust=-0.5, 
          position = 'identity')

ggsave(paste0("C:/Users/schadem/Box Sync/LAPOP Shared/working documents/maita/Coordination/IDB Online/Admin/Reporting/invites_actual_selected.png"), width = 7, height = 4)


```

```{r}
inv.resp$Rate
```








